Data Responsive-report

### 2021-02-08 GALI_2020.Rmd
data wrangling - constructing all predictors

#Panel data structure. Revenues in year t-1 as revenue 
```{r}
revenue_data <- select(gali_joined, starts_with('country') | starts_with("attention") | starts_with("inst") | ends_with("fins_revenues_m1") | ends_with("External_ID"))

revenue_data <- select(revenue_data, -fu4fins_revenues_m1)

revenue_data <- revenue_data %>% 
  gather(year, revenue, ends_with("fins_revenues_m1"))

revenue_data$year[revenue_data$year == "fins_revenues_m1"] <- -1
revenue_data$year[revenue_data$year == "fu1fins_revenues_m1"] <- 0
revenue_data$year[revenue_data$year == "fu2fins_revenues_m1"] <- 1
revenue_data$year[revenue_data$year == "fu3fins_revenues_m1"] <- 2

revenue_data$year <- as.numeric(revenue_data$year)

@@

#Initial FE regression without controls 
```{r}
gali_fe_mod <- plm(revenue ~ (attention_fc*inst_fc_gci) , 
                   data = revenue_data, 
                   index = c("country", "year"),
                   model = "within")

>>>>

#Fiancial Capital acquisiton total
```{r}
gali_joined  <- gali_joined %>% mutate(capital_raised0 = gali_joined %>% select(starts_with("inv_") & ends_with("_m1")) %>% 
                         rowSums(na.rm = TRUE))

gali_joined  <- gali_joined %>% mutate(capital_raised1 = gali_joined %>% select(starts_with("fu1inv_") & ends_with("_m1")) %>% 
                         rowSums(na.rm = TRUE))

gali_joined  <- gali_joined %>% mutate(capital_raised2 = gali_joined %>% select(starts_with("fu2inv_") & ends_with("_m1")) %>% 
                         rowSums(na.rm = TRUE))

gali_joined  <- gali_joined %>% mutate(capital_raised3 = gali_joined %>% select(starts_with("fu3inv_") & ends_with("_m1")) %>% 
                         rowSums(na.rm = TRUE))

gali_joined  <- gali_joined %>% mutate(capital_raised4 = gali_joined %>% select(starts_with("fu4inv_") & ends_with("_m1")) %>% 
                         rowSums(na.rm = TRUE))

gali_joined  <- gali_joined %>% mutate(capital_raised_tot = gali_joined %>% select(starts_with("capital_raised")) %>% 
                         rowSums(na.rm = TRUE))

@@

#Human capital acquisition 
```{r}
gali_joined  <- gali_joined %>% mutate(hr_tot = gali_joined %>%
                         select(contains("_employees")) %>% 
                         rowSums(na.rm = TRUE))
```

#Social capital acquisition 
```{r}
gali_joined <- gali_joined %>% mutate(equity_sources_tot = gali_joined %>%
                         select(contains("equityfrom")) %>% 
                         rowSums(na.rm = TRUE))
```

#Revenues
```{r}
gali_joined <- gali_joined %>% mutate(revenue_tot = gali_joined %>%
                         select(contains("revenues")) %>% 
                         rowSums(na.rm = TRUE))
```

#Exploring with plots
```{r}
ggplot(gali_joined, aes()) +
